ZCB Pricing

### 2018-08-03 ZCB Pricing .Rmd
Sensitivity tests
njhjhjh

# library(knitr)
# kable(compare_mat,align = "c")

@@

#par(mfrow = c(2,2))
#plot(1:8,senses[1,2:9])
#lines(1:8,senses[2, 2:9], col="red", type="l")

>>>>

library(xtable)
xtable(compare_mat, digits = 5)

@@

par(mfrow = c(2,2))
first <- as.vector(senses[1,2:9])
plot(1:8,first)
test <- as.vector(senses[2, 2:9])
lines(1:8,test, col="red", type="l")
